There are various operations that are performed in eCAD.
\subsection{Move}
One can move the entity from one location to other according to user requirement. One can also move multiple entities from one location to another. Also the coordinates of entites are also changed when an object is moved from one place to another. 
\subsection{Cut, Copy and Paste}
Cut, Copy and paste are one of the important features which need to be embended in any cad software. Without this any software is incomplete. We can either perform above actions from context menu or file menu.
\begin{enumerate}
\item \textbf{From Context Menu}
\begin{itemize}
\item Cut: To cut select the entity and right click on that entity then select cut. 
\item Copy: To copy select the entity and right click on that entity then select copy.
\item Paste: To paste the entity right click and select paste.
\end{itemize}
\item \textbf{From Edit Menu}
\begin{itemize}
\item Cut: To cut select the entity and  then select cut. 
\item Copy: To copy select the entity and  then select copy.
\item Paste: To paste the entity select the position on screen then select paste.
\end{itemize}
\end{enumerate}
\subsection{Delete}
We can delete the entity either by using keyboard keys or from Menu.
\begin{enumerate}
\item \textbf{From keyboard keys}:
Select an entity then press delete key.
\item \textbf{From Menu}:
Select the entity then press delete from delete menu.
\end{enumerate}
\subsection{Undo/Redo}
We can undo redo either by using shortcuts or from edit menu
\begin{enumerate}
\item \textbf{From edit menu}
\begin{itemize}
\item Undo: Click on undo to undo the previous action
\item Redo: Click on redo to redo the action.
\end{itemize}
\item \textbf{From Shorcuts}
\begin{itemize}
\item Undo: Press Ctrl+ Z to undo the previous action
\item Redo: Press Ctrl+Shift+Z to redo the action.
\end{itemize}
\end{enumerate}